Citation network analysis of urban modeling research

### 2019-08-06 paper.tex
Update on Overleaf.
.

We construct a large corpus of papers, linked through backward citations.
Our contribution relies on the following points: (i) the open dataset we make available can be of significant interest for researcher interested in urban modeling; (ii) we map a broad part of approaches to urban modeling, and more particularly clarify the relations between microsimulation, land-use transport modeling, and agent-nased modeling.
% (i) sensitivity analysis - info to reconstruct discipline with such empirical data ?
% (ii) some methodological insights depending on what we do ?
% (iii) results on urban modeling in themselves <- Maybe insist only on that ?

>>>>

We construct a large corpus of papers, linked through backward citations.
Our contribution relies on the following points: (i) the open dataset we make available can be of significant interest for researcher interested in urban modeling; (ii) we map a broad part of approaches to urban modeling, and more particularly clarify the relations between microsimulation, land-use transport modeling, and agent-based modeling.
% (i) sensitivity analysis - info to reconstruct discipline with such empirical data ?
% (ii) some methodological insights depending on what we do ?
% (iii) results on urban modeling in themselves <- Maybe insist only on that ?
